Real Estate

### 2022-10-25 src/real_estate.Rmd
psuedocode

MSA_demo_data <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=0")
city_realEstate_ata <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=359643482")
```

>>>>

MSA_demo_data <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=0")

city_realEstate_data <- read_sheet("https://docs.google.com/spreadsheets/d/10n55Gt0rySN96OGTQ2_8PzeTcX66n26sOlZBiuiAeBU/edit#gid=808954990")
```

```{r}
# aggregate yardi data into MSAs by cbsa
MSA_realEstate_data <- city_realEstate_data %>%

```

```{r}
# calculate rent to income ratio

# YoY rent change
```

```{r}
# calculate income to home price
```

```{r}

```

```{r}
# normalize everything into new data table

normalized <-

```

```{r}
# invert normalized rent to income ratio so lower values (more favorable) have higher scores

= 1- normalized score
```

```{r}
# weights from owen

# place holder column
MSA_real_estate_score <- 
  mutate

weights <- c()

```
